---
title: "Toothgrowth"
author: "IFEOLUWA"
date: "3/15/2022"
output:
  html_document: default
  pdf_document: default
---
# Dataset:Toothgrowth
## Statistical analysis
### Regression
```{r}
data(ToothGrowth)
head(ToothGrowth)
attach(ToothGrowth)
regression<-lm(len~dose)
summary(regression)
```
#### Report
##### Hypothesis
- H_o: There is no significant difference between len and dose.
- H_1: There is significant difference between len and dose.

##### Decision Rule
- p-value < 0.05, reject H_o, otherwise, fail to reject H_o.

##### Conclusion
- Since p-value(1.233e-14) < 0.05, we reject H_o. Therefore, there is  significant difference between len and supp.
- The linear regression model for the analysis is; Y = 7.4225 + 9.7636  X

### Correlation
```{r}
correlation <- cor.test(len,dose)
correlation
```
#### Report
- The analysis has a very strong positive correlation of 0.8026913.

## Graphical visualisation
```{r}
library(ggplot2)
ggplot(ToothGrowth,aes(x=len))+
geom_bar()

library(ggplot2)
ggplot(data=ToothGrowth,aes(x=len))+
geom_freqpoly(binwidth=10)

ggplot(data=ToothGrowth,aes(x=len,y=dose))+
geom_point()+
theme_bw()


ggplot(data=ToothGrowth,aes(x=len))+
geom_histogram(binwidth=10)+
theme_classic()+
labs(title="ToothGrowth", subtitle="Len and Dose")


hist(len,col="blue")
plot(len)
lines(dose)
```

## Exploratory Data Analysis
### Mean
```{r}
mean(len)
mean(dose)
```
### Variance
```{r}
var(len)
var(dose)
```
### Standard deviation
```{r}
sd(len)
sd(dose)
```


